Flip the virus:\\ A gametheoretic approach to cybersecurity

### 2015-05-17 IEEE Paper/paper/paper.tex
Conclusie aangepast

\section{Conclusions and Further Research}
\label{ch:conclusion}
In this paper we presented an adaptation of the FlipIt game to the situation of virus propagation, such as to take the delay for network infection into account. We discerned two cases. In the case the defender plays faster than the attacker, the attacker simply looses the delay. In the case the attacker plays faster, each time the defender plays in an interval, he will gain the extra time of the delay. The delay is therefore always detrimental to the benefit of the attacker. 
The formula for the second case is a slight overestimation of the defender's benefit in case the defender plays faster than the attacker period extended with the delay. When the defender plays in an interval, he will gain extra time in the next interval, since the attacker has to regain control. However, not the entire delay will be extra time, as the defender may move in again sooner. 
Further research needs to be performed to calculate the exact overestimation in this case.\\
Also the impact of the delay on Nash equilibria and the determination of optimal defender and attacher strategies needs further investigation.

>>>>

\section{Conclusions and Further Research}
\label{ch:conclusion}
In this paper we presented an adaptation of the FlipIt game to the situation of virus propagation, such as to take the delay for network infection into account. We discerned two cases. In the case the defender plays faster than the attacker, the attacker simply looses the delay. In the case the attacker plays faster, each time the defender plays in an interval, he will gain extra time of the delay. The delay is therefore always detrimental to the benefit of the attacker. 
This demonstrates that the FlipIt game can be adapted to a game with virus propagation. Further research needs to be performed to calculate the impact of the delay on Nash equilibria and the determination of optimal defender and attacker strategies.
